On the Functionality of the Multilayer Perceptron

### 2020-09-19 Thesis/Sections/TheNerualNetwork.tex
Updates to neural network

\subsubsection{Dense Layer}

@@

\paragraph*{}A neural network's job is to produce an approximation of some function $F$, which we call $F^*$. The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonable approximation of $F$. To better understand this, we turn to Tom Mitchell's explanation of a learning algorithm \cite{Goodfellow,Mitchell}:
\begin{quote}
A computer program is said to learn from experience $E$ with respect to some class of tasks $T$ and performance measure $P$, if it's performance at tasks in $T$, as measured by $P$, improves with experience $E$.
\end{quote}
Without any human intervention, a model must update itself to improve it's performance at a give task a new information is presented to it. To do this, the model must be constructed with a training procedure in mind.

\paragraph*{}We consider the set of parameters $\Theta$ as a concatenation of each applicable layer's weighting matrix and bias vector such that:
\begin{equation}
\label{eqn-Theta}
\theta = \big\{
W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)},W^{(L)}, b^{(L-1)},
\big\}
\end{equation}
We can consider each parameter as just float-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$. Each value for each parameter contributes to the output of the function. In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space.

@@

\paragraph*{}Suppose we pass a training sample $x^{0})$, with expected outcome $y$, into the neural network . For a perfectly accurate model, we expect the network's final layer, the output layer, $x^{(L-1)}$ to have activations such that $x^{(L-1)} \approx y$. Since the starting parameters of a network are often randomly generated, the prediction for training sample $x^(0)}$ is not likely to be similar to $y$ at all. We introduce a \textit{Cost Function} into our model that compares the difference between the neural output $x^{(L-1)}$ (also called $y^*$) and the desired, or expected output $y$ \cite{Goodfellow,James}.

\paragraph*{}There are various types of cost functions

@@

@@

\subsection{Chosen Model Architecture}

>>>>

\subsubsection{Dense Layer}
\label{subsec-DenseLayer}

@@

\paragraph*{}A neural network's purpose is to produce a function $F^*$ that approximates an unknown function $F$, using a set of parameters, $\Theta$. The model must have a procedure for updating the parameters in $\Theta$ to allow for a reasonably close approximation of $F$. To better understand this, we turn to Tom Mitchell's explanation of a learning algorithm \cite{Goodfellow,Mitchell}:
\begin{quote}
A computer program is said to learn from experience $E$ with respect to some class of tasks $T$ and performance measure $P$, if it's performance at tasks in $T$, as measured by $P$, improves with experience $E$.
\end{quote}
Without any human intervention, a model must update itself to improve it's performance at a give task a new information is presented to it. To do this, the model must be constructed with a training procedure in mind.

\paragraph*{}We consider the set of parameters $\Theta$ as a concatenation of each applicable layer's weighting matrix and bias vector such that:
\begin{equation}
\label{eqn-Theta}
\Theta = \big\{
W^{(0)}, b^{(0)}, W^{(1)}, b^{(1)}, W^{(2)}, b^{(2)}, ... ,W^{(L-2)}, b^{(L-2)}, W^{(L)}, b^{(L-1)},
\big\}
\end{equation}
Each parameter is floating-point number, which is stored in a weight matrix $W^{(l)}$ or bias vector $b^{(l)}$. Each value for each parameter contributes to the output of the function. Note that $W^{(l)}$ or $b^{(l)}$, itself is a parameter to train, but rather the entries that make up those structures must be trained. In increasingly complicated neural networks, there can be upwards of hundreds of thousands,or even millions of elements in $\theta$ making a neural network a functions that exist is a very high dimensional parameter-space \cite{Geron,Goodfellow}.

@@

\paragraph*{}Suppose we pass a training sample, given by the feature-vector $x^{(0)}$, with an expected outcome given by the vector $y$, into the neural network. After the network finishes processing, it's output activations are given by the vector $x^{(L-1)}$, also noted at $y^*$. For a reasonably trained model, we expect the vector $y^*$ to be "similar" to $y$, indicating that with the provided data, the network has made a valid prediction. Conversely, for an untrained network, $y^*$ is not likely to be "similar" to $y$ at all, indicating that the network has made a poor prediction.

\paragraph*{}To quantify the difference between the model's prediction,m $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $\mathbb{J}(y^*,y)$, to the network \cite{Goodfellow,James}.The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$. It returns a single value, usually a floating-point number which measures the \textit{poorness} of the prediction. A high cost value indicates a \textit{poor} prediction, and a low cost indicates a reasonable prediction.

\paragraph*{}$\mathbb{J}(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}. For this $k$-classes classification task, we choose to use a \textit{Categorical Crossentropy} (CXE) cost function. For a single predictions sample, it is defined \cite{Goodfellow}:
\begin{equation}
\label{eqn-CategoricalCrossentropy}
\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y^*_i \log_{10}(y_i) 
\end{equation}
In practice, this operation is performed over a batch of samples and an average is computed and used a \textit{batch loss} \cite{Goodfellow}.

@@

\paragraph*{}We have developed a method for quantifying the difference between a given output $y^*$ and an expected output $y$ with the inclusion of a cost function. For a trained neural network, we expect that samples consistently produce a low cost value, particularly on previous unseen inputs, which indicates that the model has appropriately \textit{generalized}. The process of training the model is to choose the parameters in $\Theta$ that allows for this behavior of the cost function. We then treat the training process of a neural network as a higher dimensional \textit{optimization} problem.

\paragraph*{}The general process of training

@@

\subsection{Chosen Model Architecture}
\label{sec-Architecture}
